Bird beak's elaboration and innovation

### 2022-05-27 Analysis/08-Figure_key.Rmd
added tree

## Phylo plot
tree_paleo <- drop.tip(tree, tip = rownames(shapespace)[which(shapespace$level1 != "Paleognathae")])
plot(ladderize(tree_paleo), show.tip.label = FALSE)

## Loading the distances from centre for each species (if adding outlines)
load("../Data/Processed/ploting_data.rda")
centroids <- ploting_data$distances_to_centre[[1]]

>>>>

## Phylo plot
## Get the tree
tree_paleo <- drop.tip(tree, tip = rownames(shapespace)[which(shapespace$level1 != "Paleognathae")])
## Ladderize
tree_paleo <- ladderize(tree_paleo)

## Get the data (in the right order)
load("../Data/Processed/ploting_data.rda")
elaborations <- ploting_data$median_elaborations[tree_paleo$tip.label]
innovations <- ploting_data$median_innovations[tree_paleo$tip.label]

## Transform them into a colour gradient
col.grad <- colorRamp(c("blue","orange"))
cols_elab <- col.grad(elaborations/max(elaborations))
cols_innov <- col.grad(innovations/max(innovations))

## Plot the tree
pdf("../Manuscript/Figures/figure_key_tree_example.pdf")
plot(tree_paleo, show.tip.label = FALSE, type = "fan")
tiplabels("", frame = "none", pch = 19, cex = 2, col = rgb(cols_elab, maxColorValue = 256), offset = -1)
tiplabels("", frame = "none", pch = 19, cex = 2, col = rgb(cols_innov, maxColorValue = 256), offset = 4)
dev.off()
